Creating optimal conditions for reproducible data analysis in \R with `fertile'\protect\thanks{The authors gratefully acknowledge contributions from Hadley Wickham, Jenny Bryan, Greg Wilson, Edgar Ruiz, and other members of the \pkg{tidyverse} team.}

### 2020-08-11 STAT-paper-template/APA/fertile.tex
restructuring for submission

\usepackage{listings}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{xspace}
\usepackage{enumitem}
\usepackage{titlesec}
\graphicspath{{images/}}
\titlespacing{\section}{0pt}{10pt plus 2pt minus 1pt}{10pt plus 2pt minus 1pt}
\titlespacing{\subsection}{0pt}{7pt plus 2pt minus 1pt}{7pt plus 2pt minus 1pt}
\titlespacing{\subsubsection}{0pt}{7pt plus 2pt minus 1pt}{7pt plus 2pt minus 1pt}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlkwd{log_report}\hlstd{()}
\end{alltt}
\begin{verbatim}
## # A tibble: 3 x 4
##   path         path_abs                             func     timestamp          
##   <chr>        <chr>                                <chr>    <dttm>             
## 1 package:pur~ <NA>                                 base::l~ 2020-08-11 18:41:48
## 2 package:for~ <NA>                                 base::l~ 2020-08-11 18:41:48
## 3 project_mic~ /Users/audreybertin/Documents/ferti~ readr::~ 2020-08-11 18:41:48
\end{verbatim}
\end{kframe}
\end{knitrout}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{fertile}\hlopt{::}\hlstd{read_csv}
\end{alltt}
\begin{verbatim}
## function (file, ...) 
## {
##     if (interactive_log_on()) {
##         log_push(file, "readr::read_csv")
##         check_path_safe(file)
##         readr::read_csv(file, ...)
##     }
## }
## <bytecode: 0x7fb540270948>
## <environment: namespace:fertile>
\end{verbatim}
\end{kframe}
\end{knitrout}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{proj_dir}
\end{alltt}
\begin{verbatim}
## [1] "project_miceps"
\end{verbatim}
\begin{alltt}
\hlstd{fs}\hlopt{::}\hlkwd{dir_ls}\hlstd{(proj_dir)} \hlopt{%>%} \hlkwd{head}\hlstd{(}\hlnum{3}\hlstd{)}
\end{alltt}
\begin{verbatim}
## project_miceps/Blot_data_updated.csv   project_miceps/CS_data_redone.csv      
## project_miceps/Estrogen_Receptors.docx
\end{verbatim}
\begin{alltt}
\hlstd{temp_dir} \hlkwb{<-} \hlkwd{sandbox}\hlstd{(proj_dir)}
\hlstd{temp_dir}
\end{alltt}
\begin{verbatim}
## /var/folders/v6/f62qz88s0sd5n3yqw9d8sb300000gn/T/RtmpuJZ1kZ/project_miceps
\end{verbatim}
\begin{alltt}
\hlstd{fs}\hlopt{::}\hlkwd{dir_ls}\hlstd{(temp_dir)} \hlopt{%>%} \hlkwd{head}\hlstd{(}\hlnum{3}\hlstd{)}
\end{alltt}
\begin{verbatim}
## /var/folders/v6/f62qz88s0sd5n3yqw9d8sb300000gn/T/RtmpuJZ1kZ/project_miceps/Blot_data_updated.csv
## /var/folders/v6/f62qz88s0sd5n3yqw9d8sb300000gn/T/RtmpuJZ1kZ/project_miceps/CS_data_redone.csv
## /var/folders/v6/f62qz88s0sd5n3yqw9d8sb300000gn/T/RtmpuJZ1kZ/project_miceps/Estrogen_Receptors.docx
\end{verbatim}
\end{kframe}
\end{knitrout}

@@

>>>>

\usepackage{listings}
\usepackage{NJDapacite}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{xspace}
\usepackage{enumitem}
\usepackage{titlesec}
\titlespacing{\section}{0pt}{10pt plus 2pt minus 1pt}{10pt plus 2pt minus 1pt}
\titlespacing{\subsection}{0pt}{7pt plus 2pt minus 1pt}{7pt plus 2pt minus 1pt}
\titlespacing{\subsubsection}{0pt}{7pt plus 2pt minus 1pt}{7pt plus 2pt minus 1pt}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlkwd{log_report}\hlstd{()}
\end{alltt}
\begin{verbatim}
## # A tibble: 3 x 4
##   path         path_abs                             func     timestamp          
##   <chr>        <chr>                                <chr>    <dttm>             
## 1 package:pur~ <NA>                                 base::l~ 2020-08-11 21:28:23
## 2 package:for~ <NA>                                 base::l~ 2020-08-11 21:28:23
## 3 project_mic~ /Users/audreybertin/Documents/ferti~ readr::~ 2020-08-11 21:28:23
\end{verbatim}
\end{kframe}
\end{knitrout}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{fertile}\hlopt{::}\hlstd{read_csv}
\end{alltt}
\begin{verbatim}
## function (file, ...) 
## {
##     if (interactive_log_on()) {
##         log_push(file, "readr::read_csv")
##         check_path_safe(file)
##         readr::read_csv(file, ...)
##     }
## }
## <bytecode: 0x7f8f8c998438>
## <environment: namespace:fertile>
\end{verbatim}
\end{kframe}
\end{knitrout}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{proj_dir}
\end{alltt}
\begin{verbatim}
## [1] "project_miceps"
\end{verbatim}
\begin{alltt}
\hlstd{fs}\hlopt{::}\hlkwd{dir_ls}\hlstd{(proj_dir)} \hlopt{%>%} \hlkwd{head}\hlstd{(}\hlnum{3}\hlstd{)}
\end{alltt}
\begin{verbatim}
## project_miceps/Blot_data_updated.csv   project_miceps/CS_data_redone.csv      
## project_miceps/Estrogen_Receptors.docx
\end{verbatim}
\begin{alltt}
\hlstd{temp_dir} \hlkwb{<-} \hlkwd{sandbox}\hlstd{(proj_dir)}
\hlstd{temp_dir}
\end{alltt}
\begin{verbatim}
## /var/folders/v6/f62qz88s0sd5n3yqw9d8sb300000gn/T/RtmpGDaHPo/project_miceps
\end{verbatim}
\begin{alltt}
\hlstd{fs}\hlopt{::}\hlkwd{dir_ls}\hlstd{(temp_dir)} \hlopt{%>%} \hlkwd{head}\hlstd{(}\hlnum{3}\hlstd{)}
\end{alltt}
\begin{verbatim}
## /var/folders/v6/f62qz88s0sd5n3yqw9d8sb300000gn/T/RtmpGDaHPo/project_miceps/Blot_data_updated.csv
## /var/folders/v6/f62qz88s0sd5n3yqw9d8sb300000gn/T/RtmpGDaHPo/project_miceps/CS_data_redone.csv
## /var/folders/v6/f62qz88s0sd5n3yqw9d8sb300000gn/T/RtmpGDaHPo/project_miceps/Estrogen_Receptors.docx
\end{verbatim}
\end{kframe}
\end{knitrout}

@@

\section*{Data Availability Statement}
The sample project ("project\_miceps") and package code associated with this paper can be found in the "R" and "tests" folders at \href{https://github.com/baumer-lab/fertile}{https://github.com/baumer-lab/fertile}.
